---
title: "Using the giantbomb Package"
author: "Jonathan De Troye"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using the giantbomb Package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction

The `giantbomb` package provides access to the [GiantBomb API](https://www.giantbomb.com/api/) which gives information on video games, reviews, companies, and other related content.

# Installation

You can install the package from GitHub using the `devtools` package:

```{r, eval=FALSE}
devtools::install_github("detroyejr/giantbomb")
```

# API key

Before you can begin to use the `giantbomb` package, you will need to [sign up](https://www.giantbomb.com/signup/) to receive an API key. Once you login, your key will appear on the [main API page](https://www.giantbomb.com/api/).

Once you have your key, you can either pass it as a string to the `api_key` function parameters or set the `GB_KEY` environment variable.

```{r, eval=FALSE}
Sys.setenv("GB_KEY" = 'YOUR_API_KEY')
```

The function `gb_key()` will look in the system environment for a variable with that name.

# Basic usage

## Getting a list of games

You can retrieve a list of games using the `gb_games` function. Here is an example:

```{r}
library(giantbomb)

# Get list of games
games <- gb_games(n = 10, field_list = c("date_added", "name"))
print(games)
```

## Getting a list of companies

You can retrieve a list of companies using the `gb_companies` function. Here is an example:

```{r}
# Get list of companies
companies <- gb_companies(n = 10, field_list = c("date_added", "name"))
print(companies)
```

# Filtering and sorting

You can filter and sort the results using the `filter` and `sort` parameters. Here are some examples:

## Filtering by name and sorting by date added

```{r}
# Filter by name and sort by date_added
bioshock_games <- gb_games(
  n = 10,
  filter = "name:bioshock",
  sort = "date_added:desc",
  field_list = c("name", "date_added")
)
print(bioshock_games)
```

## Filtering companies by name and sorting by date added

```{r}
# Filter companies by name and sort by date_added
companies_2k <- gb_companies(
  n = 10,
  filter = "name:2k",
  sort = "date_added:asc",
  field_list = c("name", "date_added")
)
print(companies_2k)
```

# Additional Examples

## Getting a list of characters

You can retrieve a list of characters using the `gb_characters` function. Here is an example:

```{r}
# Get list of characters
characters <- gb_characters(n = 10, field_list = c("date_added", "name"))
print(characters)
```

## Getting a list of reviews

You can retrieve a list of reviews using the `gb_reviews` function. Here is an example:

```{r}
# Get list of reviews
reviews <- gb_reviews(n = 10, field_list = c("date_added", "name"))
print(reviews)
```

## Getting a list of platforms

You can retrieve a list of platforms using the `gb_platforms` function. Here is an example:

```{r}
# Get list of platforms
platforms <- gb_platforms(n = 10, field_list = c("date_added", "name"))
print(platforms)
```

# Summary

The `giantbomb` package provides a convenient way to access the GiantBomb API and retrieve information about video games, reviews, companies, and other related content. For more examples and detailed information, please refer to the function documentation.
